An active sampling model of mental rotation

### 2014-01-26 man/cogsci-2014/cogsci-2014.tex
Input analysis tex files
Update figures, more work on methods

@@

\subsection{Participants}

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/response-times.pdf}
    \caption{\textbf{Response times.}}
    \label{fig:response-times}
  \end{center}
\end{figure*}

We recruited \TODO{N} participants on Amazon's Mechanical Turk. Each
participant was paid \$1.00 for approximately 15 minutes of work. Out
of these participantsm \TODO{N\% (N)} were included in our
analyses. The others were excluded either because of an experimental
error (\TODO{N\% (N)}), because they had already compelted a previous
version of the experiment (\TODO{N\% (N)}), or because they failed a
comprehension check (\TODO{N\% (N)}).

@@

The experiment consisted 210 total trials: of one block of 10 practice
trials followed by two blocks of 100 experiment trials. Within a
block, trials were presented in a random order.

@@

On each trial, particpants were instructed to press the `b' key to
begin and to focus on the fixation cross that appeared for \TODO{N}
milliseconds afterwards. The two images were then presented
side-by-side, each at 300px $\times$ 300px, and participants could
press `s' to indicate they thought the images depicted the same
object, or `d' to indicate they thought the images depicted flipped
objects.

@@

@@

\begin{figure}[t]
  \centering
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial-vs-accuracy.pdf}}%
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial-vs-time.pdf}}
  \caption{\textbf{Effect of learning.}}
  \label{fig:learning}
\end{figure}

>>>>

\input{../../results/D/response_time.tex}
\input{../../results/D/response_time_corrs.tex}
\input{../../results/D/accuracy.tex}
\input{../../results/D/accuracy_corrs.tex}
\input{../../results/D/trial_time_corrs.tex}
\input{../../results/D/trial_accuracy_corrs.tex}

@@

\begin{figure*}[t]
  \begin{center}
    \includegraphics[width=\textwidth]{../../figures/D/response_time.pdf}
    \caption{\textbf{Response times.}}
    \label{fig:response-times}
  \end{center}
\end{figure*}

@@

We recruited 247 participants on Amazon's Mechanical Turk. Each
participant was paid \$1.00 for approximately 15 minutes of work,
consisting of one block of 10 practice trials followed by two blocks
of 100 experiment trials. Within a block, trials were presented in a
random order.

@@

On each trial, particpants were instructed to press the `b' key to
begin and to focus on the fixation cross that appeared for 750
milliseconds afterwards. The two images were then presented
side-by-side, each at 300px $\times$ 300px, and participants could
press `s' to indicate they thought the images depicted the same
object, or `d' to indicate they thought the images depicted flipped
objects.

@@

\section{Analysis}

Out of the 247 participants, 200 (81\%) were included in our
analyses. Of the rest, we excluded 10 (4\%) because of an experimental
error, 6 (2.4\%) because they had already compelted a previous version
of the experiment, and 31 (12.6\%) because they failed a comprehension
check. A participant was marked as passing the comprehension check if
they answered at least 85\% of ``easy'' trials correctly. ``Easy''
trials were defined to be those for which the presented shapes
differed by a rotation of no more than 20 degrees.

We ran model simulations for the same stimuli that participants
viewed. We ran 10 samples of each stimulus under the Oracle model, and
100 samples of each stimulus for the Threshold, Hill Climbing, and
Bayesian Quadrature models, with the exception of stimuli where
$\theta=0$ or $\theta=180$, in which case we ran double the number of
samples.

For all analyses (except those of accuracy), confidence intervals were
computed using a bootstrap analysis with 10000 bootstrap samples. For
analyses of accuracy, confidence intervals were computed from a
binomial proportion with a Jeffrey's beta prior.

@@

\begin{figure}[t]
  \centering
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial_accuracy.pdf}}%
  \subfloat{\includegraphics[width=0.25\textwidth]{../../figures/D/trial_time.pdf}}
  \caption{\textbf{Effect of learning.}}
  \label{fig:learning}
\end{figure}
